% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}

  I would like to thank my supervisor Nick Kingsbury, who has dedicated so
  much of his time to support and help my research. He has not only been instructing and
  knowledgeable, but very kind and supportive. I also could not have asked for a
  better and more diligent proof-reader. I will fondly remember the time
  we spent together brainstorming ideas in his beautiful room in Trinity
  College.
  
  I would also like to thank my advisor-cum-supervisor Joan Lasenby, who has always
  been very friendly and supportive, and for `adopting' me when Nick officially
  retired.

  I would like to thank the Division F computing staff, in particular Phill
  Richardson, Peter Grandi and Raf Czlonka. They spent many hours answering my
  support emails, installing packages and bringing
  the servers back online quickly whenever they went down. I know I made many
  more support requests than the average student, and I appreciate the effort
  they put in.

  I would like to say thank you to my excellent lab friends, I could not have asked for a better group of
  people to do my research alongside. In particular, thank you: Adam Greig and Rich Wareham
  for inspiring me to be a better programmer; Sam Duffield, Jacob Vorstrup and Oliver Bonner 
  for your support, friendship and lectures on \emph{tea}; Hugo Hadfield for inspiring me to 
  \texttt{import numba}; Mahed Abroshan and Ehsan Asadi for
  motivating me to be a better chess player and problem solver; Parham Bouroumand, 
  Jiaming Liang, Kuan Hseih, James Li, Edmund Bonikowski and the many other
  excellent people in SigProc. I would particularly like to thank Amarjot Singh
  and Jos van der Westhuizen. Amarjot for his collaboration and inspiration; and Jos, 
  for his friendship and his infectious ambition.
  
  I sincerely thank Trinity College for both being my alma mater and
  for sponsoring me to do my research. Without their generosity I would not be
  here.

  And finally I would like to thank my loving fianc\'ee Cordelia O'Connell, and my parents
  Bill and Mary-Rose for their ongoing emotional support.
\end{acknowledgements}
