\section{Experiments and Preliminary Results}\label{sec:ch6:results}
To examine the effectiveness of our convolutional layer, we do a simple
experiment on CIFAR-10 and CIFAR-100. For simplicity, we compare the performance
using a simple yet relatively effective convolutional architecture - LeNet
\cite{lecun_gradient-based_1998}. LeNet has 2 convolutional layers of spatial
size $5\x 5$ followed by 2 fully connected layers and a softmax final layer. We
swap both these convolutional layers out for two of our proposed wavelet gain
layers (keeping the ReLU between them). As CIFAR has very small spatial size, we
only take a single scale $\DTCWT$. Therefore each gain layer has $6$ complex
gains for the 6 subbands, and a $3\x 3$ real gain for the lowpass (a total of
$21C$ parameters vs $25C$ for the original system). We train both networks for
200 epochs with Adam \cite{kingma_adam:_2014} optimizer with a constant learning
rate of $10^{-3}$ and a weight decay of $10^{-5}$. The code is available at
\cite{cotter_dtcwt_2018}. \autoref{tab:results} shows the mean of the
validation set accuracies for 5 runs. The different columns represent
undersampled training set sizes (with 50000 being the full training set).
When undersampling, we keep the samples per class constant. We see our
system perform only very slightly worse than the standard convolutional
layer. 

\begin{table}[]
  \centering
{\renewcommand{\arraystretch}{1.2}
  \captionsetup{width=\textwidth}
  \caption{Comparison of LeNet with standard convolution to our proposed method
    which learns in the wavelet space (WaveLenet) on CIFAR-10 and CIFAR-100.
  Values reported are the average top-1 accuracy (\%) rates for different train
  set sizes over 5 runs.}
\begin{tabular}{cccccccc}
  \specialrule{.1em}{.1em}{.1em} 
  & Train set size & 1000 & 2000 & 5000 & 10000 & 20000 & 50000 \\ \specialrule{.1em}{.1em}{.1em} 
  \multicolumn{1}{l}{\multirow{2}{*}{CIFAR-10}} & LeNet & 
    48.5 & 52.4 & 59.5 & 65.0 & 69.5 & 73.3\\ \cline{2-8}
  \multicolumn{1}{l}{} & WaveLeNet & 
    47.3 & 52.1 & 58.7 & 63.8 & 68.0 & 72.4\\ \hline
  \multicolumn{1}{l}{\multirow{2}{*}{CIFAR-100}} & LeNet & 
    11.1 & 15.8 & 23.1 & 29.5 & 34.4 & 41.1  \\ \cline{2-8}
  \multicolumn{1}{l}{} & WaveLeNet & 
    11.1 & 15.4 & 23.2 & 28.4  & 33.9 & 39.6 \\ \specialrule{.1em}{.1em}{.1em} 
\end{tabular}\label{tab:results}
}
\end{table}
