\section{Method}\label{sec:ch6:method}

\input{\path/figure1}

In a standard convolutional layer, an input with $C$ channels, $H$ rows and $W$
columns is $X \in \reals[C\x H\x W]$, which is then convolved with $F$ filters
of spatial size $K$ - $w \in \reals[F \x C\x K\x K]$, giving $Y \in \reals[F\x
H\x W]$. In many systems like \cite{krizhevsky_imagenet_2012, he_deep_2015}, the
first layer is typically a selection of bandpass filters, selecting edges with
different orientations and center frequencies. In the wavelet space this would
be trivial - take a decomposition of each input channel and keep individual
subbands (or equivalently, attenuate other bands), then take the inverse wavelet
transform.  \autoref{fig:ch6:dtcwt_bands} shows the frequency space for the
$\DTCWT$ and makes it clearer as to how this could be done practically for a two
scale transform. To attenuate all but say the $15 \degs$ band at the first scale
for the first input channel, we would need to have $13C$ gains for the 13
subbands and $C$ input channels, $13C-1$ of which would be zero and the
remaining coefficient one.

Instead of explicitly setting the gains, we can randomly initialize them and use
backpropagation to learn what they should be. This gives us the power to learn
more complex shapes rather than simple edges, as we can mix the regions of the
frequency space per input channel in an arbitrary way. 

\subsection{Forward propagation}
\autoref{fig:ch6:fwd_bwd} shows the block diagram using $Z$-transforms for
a single band of our system (it is based on Figure~4 in
\cite{kingsbury_complex_2001}). To keep things simple for the rest of
\autoref{sec:ch6:method} the figure shown is for a 1-D system; it is relatively
straightforward to extend this to 2-D\cite{selesnick_dual-tree_2005}. The
complex analysis filter (taking us into the wavelet domain) is $P(z)
= \frac{1}{2}\left(A(z)+jB(z)\right)$ and the complex synthesis filter
(returning us to the pixel domain) is $Q(z) = \frac{1}{2}\left(C(z)
  - jD(z)\right)$ where $A,B,C,D$ are real.  If $G(z) = G_r(z) + jG_i(z) = 1$
  then the end-to-end transfer function is (from section 4 of
\cite{kingsbury_complex_2001}):

\begin{equation}\label{eq:ch6:end_to_end1}
\frac{Y(z)}{X(z)} = \frac{2}{M}\left(P(z)Q(z) + P^*(z)Q^*(z)\right)
\end{equation}

where $P, Q$ have support only in the top half of the Fourier plane and $P^*,
Q^*$ are $P$ and $Q$ reflected in the horizontal frequency axis. Examples of
$P(z)Q(z)$ for different subbands of a 2-D $\DTCWT$ have spectra shown in
\autoref{fig:ch6:dtcwt_bands_freq}, $P^*(z)Q^*(z)$ make up the missing half of
the frequency space.\\ 

Modifying this from the standard wavelet equations by
adding the subband gains $G_r(z)$ and $G_i(z)$, the transfer function becomes:
\begin{equation}\label{eq:ch6:end_to_end2}
    \frac{Y(z)}{X(z)} = \frac{2}{M} \left[ \right. G_r(z^M) \left( P(z)Q(z) + P^*(z)Q^*(z) \right) +  
      \left. jG_i(z^M) \left(P(z)Q(z)-P^*(z)Q^*(z) \right) \right]
\end{equation}

\subsection{Backpropagation}
We start with the commonly known property that for a convolutional block, the
gradient with respect to the input is the gradient with respect to the output
convolved with the time reverse of the filter. More formally, if 
$Y(z) = H(z) X(z)$:
\begin{equation}\label{eq:ch6:backprop}
\Delta X(z) = H(z^{-1}) \Delta Y(z)
\end{equation}
where $H(z^{-1})$ is the $Z$-transform of the time/space reverse of $H(z)$,
$\Delta Y(z) \triangleq \dydx{L}{Y}(z)$ is the gradient of the loss with respect
to the output, and $\Delta X(z) \triangleq \dydx{L}{X}(z)$ is the gradient of
the loss with respect to the input. If H were complex, the first term in
\autoref{eq:ch6:backprop} would be $\bar{H}(1/\bar{z})$, but as each individual
block in the $\DTCWT$ is purely real, we can use the simpler form. 

Assume we already have access to the quantity $\Delta Y(z)$ (this is the input
to the backwards pass). \autoref{fig:ch6:bwd_pass} illustrates the
backpropagation procedure. An interesting result is that the backwards pass of
an inverse wavelet transform is equivalent to doing a forward wavelet
transform.\footnote{As shown in \autoref{fig:ch6:bwd_pass}, the analysis and
synthesis filters have to be swapped and time reversed. For orthogonal wavelet
transforms, the synthesis filters are already the time reverse of the analysis
filters, so no change has to be done. The q-shift filters of the $\DTCWT$
\cite{kingsbury_design_2003} have this property.} Similarly, the backwards pass
of the forward transform is equivalent to doing the inverse transform. The
weight update gradients are then calculated by finding 
$\Delta W(z) = \DTCWT\left\{ \Delta Y(z) \right\}$ and then convolving with the 
time reverse of the saved wavelet coefficients from the forward pass - $V(z)$.

\begin{gather}
  \Delta G_r(z) = \Delta W_r(z) V_r(z^{-1}) + \Delta W_i(z) V_i(z^{-1})  \label{eq:ch6:gr_update}\\
  \Delta G_i(z) =  -\Delta W_r(z) V_i(z^{-1}) + \Delta W_i(z) V_r(z^{-1})  \label{eq:ch6:gi_update} 
\end{gather}

Unsurprisingly, the passthrough gradients have similar form to
\autoref{eq:ch6:end_to_end2}:
\begin{equation}\label{eq:ch6:passthrough}
    \Delta X(z) = \frac{2\Delta Y(z)}{M} \left[G_r(z^{-M})\left( PQ + P^*Q^* \right)\right. + 
      \left. jG_i(z^{-M}) \left(PQ-P^*Q^* \right) \right] 
\end{equation}
where we have dropped the $z$ terms on $P(z), Q(z), P^*(z), Q^*(z)$ for brevity.

Note that we only need to evaluate equations
~\ref{eq:ch6:gr_update},\ref{eq:ch6:gi_update},\ref{eq:ch6:passthrough} over the
support of $G(z)$ i.e., if it is a single number we only need to calculate
$\left.\Delta G(z)\right\rvert_{z=0}$.


\subsection{Memory Cost}
Again considering a two scale transform --- instead of learning $w\in \reals[F
\x C\x K\x K]$ we learn complex gains at the two scales, and a real gain for the
real lowpass:

\begin{eqnarray*}
  g_1 &\in& \complexes[F\x C\x 6\x 1\x 1] \\
  g_2 &\in& \complexes[F\x C\x 6\x 1\x 1] \\
  g_{lp} &\in& \reals[F\x C\x 1\x 1]
\end{eqnarray*}

We have set the spatial dimension to be $1\x 1$ to show that this gain is
identical to a $1\x 1$ convolution over the complex wavelet coefficients. If we
wish, we can learn larger spatial sizes to have more complex
attenuation/magnification of the subbands. We also can use more/fewer than
2 wavelet scales.  At first glance, we have increased our parameterization by
a factor of 25 (13 subbands, of which all but the lowpass are complex), but
each one of these gains affects a large spatial size. For the first scale, the
effective size is about $5\x 5$ pixels, for the second scale it is about $15\x
15$.

\subsection{Computational Cost}
A standard convolutional layer needs $K^2 F$ multiplies per input pixel (of
which there are $C\x H\x W$). In comparison, the wavelet gain method does a set
number of operations per pixel for the forward and inverse transforms, and then
applies gains on subsampled activations. For a 2 level $\DTCWT$ the transform
overhead is about 60 multiplies for both the forward and inverse transform. It
is important to note that unlike the filtering operation, this does not scale
with $F$. The learned gains in each subband do scale with the number of output
channels, but can have smaller spatial size (as they have larger effective
sizes) as well as having fewer pixels to operate on (because of the decimation).
The end result is that as $F$ and $C$ grow, the overhead of the $C$ forward and
$F$ inverse transforms is outweighed by cost of $FC$ mixing processes, which
should in turn be significantly less than the cost of $FC$ $K\x K$ standard
convolutions for equivalent spatial sizes.

\input{\path/figure2}

\subsection{Examples}
\autoref{fig:ch6:example_impulses} show example impulse responses of our layer.
These impulses were generated by randomly initializing both the real and
imaginary parts of $g_2 \in \complexes[6\x 1\x 1]$ from $\mathcal{N}(0,1)$ and
$g_1, g_{lp}$ are set to 0. I.e. each shape has 12 random variables. It is good
to see that there is still a large degree of variability between shapes. Our
experiments have shown that the distribution of the normalized cross-correlation
between 512 of such randomly generated shapes matches the distribution for
random vectors with roughly 11.5 degrees of freedom.

